HBCC - ACC - STG - DREAM - FEATURECOUNTS - GRCh38 - CQN

### 2020-04-05 cmc-rnaseq-de/HBCC_ACC-STG_FEATURECOUNTS_GRCh38_CQN_Sparse.Rmd
fix outlier plot typo

plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, "SampleID")) %>%
    tidyr::separate(Dx.Tissue, c('Dx','Tissue'), sep = '_') %>%
  dplyr::mutate(label = SampleID) %>% 
  dplyr::mutate(label = ifelse((label %in% outliers), label, NA)) %>% 
  tidyr::separate(Dx.Tissue, c('Dx','Tissue'), sep = '_') %>% 
  dplyr::mutate(Institution = "NIMH-HBCC")

>>>>

plotdata <- left_join(plotdata, rownameToFirstColumn(COVARIATES, "SampleID")) %>%
  tidyr::separate(Dx.Tissue, c('Dx','Tissue'), sep = '_') %>%
  dplyr::mutate(label = SampleID) %>% 
  dplyr::mutate(label = ifelse((label %in% outliers), label, NA)) %>% 
  dplyr::mutate(Institution = "NIMH-HBCC")
